Comparing methods for estimating parasite-induced host mortality from distributional data: implementation and limitations

### 2015-05-07 docs/parasite_mortatlity_manuscript.tex
Edited manuscript supplementary material and made a few changes to figures

Using both the pre-mortality and post-mortality simulated datasets,  we assumed
that the values of $N_p$, $\mu_p$, and $k_p$ were known and tested the ability of both methods to correctly determine whether or not PIHM was occurring.  While this scenario is unrealistic because the parameters $N_p$,
$\mu_p$, and $k_p$ are always unknown, we implemented this scenario as a baseline to
establish the efficacy of the methods independent of the estimates of $N_p$, $\mu_p$ and $k_p$.  For the Adjei Method, $N_p$, $\mu_p$, and $k_p$ are estimated using the Crofton Method, while $\mu_p$ and $k_p$ in the Likelihood Method can be estimated jointly with $a$ and $b$ or via the Crofton Method.   If a
method could not correctly predict whether or not PIHM was occurring under these idealistic conditions, we considered this strong evidence of the unreliability of this method.

We used three different values of $\mu_p$ (10, 50, 100) and for each $\mu_p$ we examined three different survival functions that had graduate, moderate, and steep decreases in the host survival with increasing parasite intensity (Figure \ref{fig:surv}).  For a given $\mu_p$, each survival function had the same $LD_{50}$ ([$\mu_p = 10$, $LD_{50} = 7.39$], [$\mu_p = 50$, $LD_{50} = 35.57$], [$\mu_p = 100$, $LD_{50}= 77.3$]),  but different values of $a$ and $b$.  We examined each $\mu_p$-survival function pair at  three levels of parasite
aggregation, $k_p = 0.1$, 0.5, and 1 --- realistic values of parasite aggregation in natural populations \citep{Shaw1998}.  For each of these parameter
combinations we simulated 150 datasets and tested the probability of each method incorrectly identifying PIHM in the pre-mortality dataset (Type I error) and correctly identifying PIHM in the post-mortality dataset (power).  For each method, we used a likelihood ratio test to determine whether the full model with PIHM provided a significantly better fit than the reduced model without PIHM at significance level $\alpha = 0.05$.  We tested each parameter combinations for pre-mortality population sizes of $N_p$ = [50, 100, 200, 300, 400, 500]. $N_p$ is not technically the sample size on which the methods are being
tested on the post-mortality data because PIHM reduces $N_p$ for each simulated
dataset.  We therefore used the average number of surviving hosts over all 150 simulations for a given parameter combination as our measure of sample size in the power simulations.\\

@@

@@

% Change statistical alpha to something else so I don't confuse it with pathogenecity alpha.

@@

% What figures do we want to show?  Represent figures in a single frame? Pick one that shows the general pattern? Maybe drop the a figure to the Supplement?

% Crop Figure 2 and merge Fig 3-4 to have 4 panels.

% Fiddle with Figure 1 to make it a plate in The new figure 2? Inset it in some way.

% Figure 3: Just focus on small (100) size and vary mu and k and see what happens. (Chose steep survival function for LD50)

@@

The Adjei Method detected PIHM in 9 of the 10 datasets (Table \ref{table:pihm}), consistent with our simulation results that the Adjei Method has a high Type I error rate [additional data? to emphasize this point. Raccoon data?].

@@

Using simulated data, we found that the Likelihood Method always out performs the Adjei Method. For simply detecting the presence of PIHM, the Likelihood
Method is both more powerful and has fewer false detection events (Type I
errors) [tense?].  When both methods were applied to published datasets previously used
in PIHM analyses, the Adjei Method tended to detect PIHM where it had not previously been
reported, consistent with the high Type I error rate observed in our
simulations. The Likelihood Method is also more precise and less
biased in calculations of both the parasite $LD_{50}$ and host survival curve over the parameter values we considered.
However, while only the Likelihood Method produces precise and unbiased $LD_{50}$
estimates, neither method can provide unbiased estimates of the host survival
function at realistic sample sizes.  These simulations demonstrate that
the Likelihood Method is more powerful and precise than the previously propose Adjei Method.

Although superior to the Adjei Method, the Likelihood Method may still not always be
applicable to real data.  The Likelihood Method requires relatively large
sample sizes (n>50-100) [Are these relatively large? They seem small to me], that although reasonable
to obtain for invertebrates or small fish may be completely unfeasible for many
vertebrates, particularly the species of conservation concern where addressing
the impact of parasitism would be most important [citation?]. An even larger sample size is
required to capture the full parasite distribution when parasites are highly
aggregated, mean infection intensity is high, or parasite prevalence is low [same as aggregation],
all of which are common in many parasitic helminths.  Low parasite-induced host
mortality, as might be predicted in many definitive hosts, may also be very
difficult to detect and require impossibly large sample sizes. And, even
when sample size is sufficient, these methods can only detect PIHM is the host
survival curve is non-linear \citep{Lanciani1989}. Most host-parasite models assume a linear
relationship between survival and infection intensity \citep{AndersonandMay1978,McCallum2000a}, however
nonlinear survival functions are not uncommon in empirical host-parasite
systems \citep{Benesh2011}.  And, while linear functions make PIHM undetectable, at the other extreme, steep, non-linear survival curves produce severely biased estimates of the survival function. Even the Likelihood Method is probably limited to
detecting PIHM and estimating $LD_{50}$ in systems where greater than 50 hosts can be
collected, parasites are common and only moderately aggregated, and
substantial host mortality occurs at relatively low parasite intensity.

@@

\caption{A) Five potential shapes for a host-survival functions. In the simulations we used a gradual survival function (dotted line), and moderate survival function (dashed line), and a steep survival function (solid line). The linear and immediate survival functions represent two potential extremes. For each of these survival functions and the parameter combinations described in the main text, we tested the Type I Error and Power of the Likelihood Method and Adjei Method. B) gives the Type I Error of each method over a range of pre-mortality sample sizes with $\mu_p = 50$ and $k_p = 0.5$. The red line shows the pre-set significance level of 0.05. C) gives the Power of each method for detecting PIHM over a range of post-mortality sample sizes for $\mu_p = 50$ and $k_p = 0.5$.  In general, the Likelihood Method has higher power and lower Type I Error than the Adjei Method.  See the SI X Fig X - X for Type I Error and Power results for all parameter combinations.}

@@

    \caption{Bias and precision (coefficient of variation) for the Likelihood Method and Adjei Method estimates of the $a$ parameter and the $LD_{50}$ of the host survival function based on simulated PIHM data over a range of post-mortality sample sizes. The pre-mortality parameters for this simulation were $\mu_p = 50$ and $k_p = 0.5$.  The figure shows the simulations for three different host survival functions (gradual, moderate, and steep) with the same $LD_{50}$.  Bias and precision results for all other parameter combinations can be found in Fig X - X in SI X.}

    \label{fig:question2}
\end{figure}

% \begin{figure}
%     \includegraphics[width=\textwidth]{/Users/mqwilber/Repos/parasite_mortality/results/conceptual_fig.pdf}

%     \caption{Five potential shapes for a host-survival functions. PIHM should be easier to detect for steeper host survival functions \citep{Lanciani1989}, but we may expect the bias in the parameter estimates to increase as it becomes increasingly difficult to distinguish between steep survival functions.}
%     \label{fig:surv}
% \end{figure}

% \begin{figure}

%     \includegraphics[width=\textwidth]{/Users/mqwilber/Repos/parasite_mortality/results/typeIpower_figure_for_mu10}

%     \caption{The Type I error rate and the power of the Likelihood Method (solid line) and the Adjei Method (dashed lines) when $\mu_p = 10$ for various shapes of the host survival function and levels of aggregation $k_p$.  The first column gives the Type I error rate of each method for falsely detecting PIHM when none is present.  The red line gives the the pre-set Type I error rate of $\alpha = 0.05$.  The second column gives the power of a given method to detect PIHM when it is actually occurring. }
%     \label{fig:typeI10}

% \end{figure}

% \begin{figure}

%     \includegraphics[width=\textwidth]{/Users/mqwilber/Repos/parasite_mortality/results/bais_prec_figure_for_ld50_mu10}

%     \caption{The bias and the precision of the Likelihood Method (solid line) and the Adjei Method (dashed lines) when $\mu_p = 10$ for various shapes of the host survival function and levels of aggregation $k_p$ when estimating $LD_{50}$.  The first column gives the bias of each method's $LD_{50}$ estimate over 150 simulations. The second column gives the precision of each method's $LD_{50}$ estimate over 150 simulations.}

%     \label{fig:biasld50}

% \end{figure}

% \begin{figure}

%     \includegraphics[width=\textwidth]{/Users/mqwilber/Repos/parasite_mortality/results/bais_prec_figure_for_a_mu10}

%     \caption{The bias and the precision of the Likelihood Method (solid line) and the Adjei Method (dashed lines) when $\mu_p = 10$ for various shapes of the host survival function and levels of aggregation $k_p$ when estimating the $a$ parameter of the host survival function.  The first column gives the bias of each method's $a$ estimate over 150 simulations. The second column gives the precision of each method's $a$ estimate over 150 simulations.}

%     \label{fig:biasa}

% \end{figure}

>>>>

Using both the pre-mortality and post-mortality simulated datasets,  we assumed
that the values of $N_p$, $\mu_p$, and $k_p$ were known and tested the ability
of both methods to correctly determine whether or not PIHM was occurring.
While this scenario is unrealistic because the parameters $N_p$, $\mu_p$, and
$k_p$ are always unknown, we implemented this scenario as a baseline to
establish the efficacy of the methods independent of the estimates of $N_p$,
$\mu_p$ and $k_p$.  If a method could not correctly predict whether or not PIHM
was occurring under these idealistic conditions, we considered this strong
evidence of the unreliability of this method.  For the Adjei Method, $N_p$,
$\mu_p$, and $k_p$ are estimated using the Crofton Method, while $\mu_p$ and
$k_p$ in the Likelihood Method can be estimated jointly with $a$ and $b$ or via
the Crofton Method (SI X).

We used three different values of $\mu_p$ (10, 50, 100) and for each $\mu_p$ we examined three different survival functions that had graduate, moderate, and steep decreases in the host survival with increasing parasite intensity (Figure \ref{fig:surv}).  For a given $\mu_p$, each survival function had the same $LD_{50}$ ([$\mu_p = 10$, $LD_{50} = 7.39$], [$\mu_p = 50$, $LD_{50} = 35.57$], [$\mu_p = 100$, $LD_{50}= 77.3$]),  but different values of $a$ and $b$.  We examined each $\mu_p$-survival function pair at  three levels of parasite
aggregation, $k_p = 0.1$, 0.5, and 1 --- realistic values of parasite aggregation in natural populations \citep{Shaw1998}.  For each of these parameter
combinations we simulated 150 datasets and tested the probability of each method incorrectly identifying PIHM in the pre-mortality dataset (Type I error) and correctly identifying PIHM in the post-mortality dataset (power).  For each method, we used a likelihood ratio test to determine whether the full model with PIHM provided a significantly better fit than the reduced model without PIHM at significance level of 0.05.  We tested each parameter combinations for pre-mortality population sizes of $N_p$ = [50, 100, 200, 300, 400, 500]. $N_p$ is not technically the sample size on which the methods are being
tested on the post-mortality data because PIHM reduces $N_p$ for each simulated
dataset.  We therefore used the average number of surviving hosts over all 150 simulations for a given parameter combination as our measure of sample size in the power simulations.\\

@@

\subsection*{Efficacy of the Likelihood Method with unknown pre-mortality parameters}

In the above simulations, we tested the power of the Likelihood Method in the ideal scenario when the pre-mortality parameters were known (or estimated independently via the Crofton Method).  In this simulation, test the ability of the Likelihood Method to correctly identify PIHM and estimate $LD_50$ when the pre-mortality parameters are not known. The simulations in the previous sections showed that the Likelihood method was highly effective at identifying PIHM and the $LD_{50}$ when $\mu_p = 10$ and $k_p = 1$, and as an illustrative example of the limitations of the Likelihood Method, we only use these pre-mortality values when simulating the dataset.

@@

@@

@@

The Adjei Method detected PIHM in 9 of the 10 datasets (Table \ref{table:pihm}), consistent with our simulation results that the Adjei Method has a high Type I error rate.

@@

Using simulated data, we found that the Likelihood Method always out performed the Adjei Method. For simply detecting the presence of PIHM, the Likelihood
Method was both more powerful and had fewer false detection events (Type I
errors).  When both methods were applied to published datasets previously used
in PIHM analyses, the Adjei Method tended to detect PIHM where it had not previously been
reported, consistent with the high Type I error rate observed in our
simulations. The Likelihood Method was also more precise and less
biased in calculations of both the parasite $LD_{50}$ and host survival curve over the parameter values we considered.
However, while only the Likelihood Method produced precise and unbiased $LD_{50}$
estimates, neither method could provide unbiased estimates of the host survival
function at realistic sample sizes.  These simulations demonstrate that
the Likelihood Method is more powerful and precise than the previously propose Adjei Method.

Although superior to the Adjei Method, the Likelihood Method may still not
always be applicable to real data.  Our simulations showed when the when pre-
mortality parameters were not set a priori, the Likelihood Method needed at
least X samples to have 80\% power and for steep survival functions and even
more as the survival function became more gradual. While these sample sizes are
reasonable for hosts such as invertebrates or small fish, they are completely
unfeasible for many vertebrates, particularly the species of conservation
concern where addressing the impact of parasitism would be most important. An
even larger sample size would be required to capture the full parasite
distribution when parasites are highly aggregated, mean infection intensity is
high, or parasite prevalence is low [same as aggregation], all of which are
common in many parasitic helminths.  Low parasite-induced host mortality, as
might be predicted in many definitive hosts, may also be very difficult to
detect and require impossibly large sample sizes. And, even when sample size is
sufficient, these methods can only detect PIHM when the host survival curve is
non-linear \citep{Lanciani1989}. Most host-parasite models assume a linear
relationship between survival and infection intensity
\citep{AndersonandMay1978,McCallum2000a}, however non-linear survival functions
are not uncommon in empirical host-parasite systems \citep{Benesh2011}.  And,
while linear functions make PIHM undetectable, at the other extreme, steep,
non-linear survival curves produce severely biased estimates of the survival
function. Give the interaction between all of these different factors, the
Likelihood Method is probably limited to detecting PIHM and estimating
$LD_{50}$ in systems where greater 100 hosts can be collected, parasites are
common and only moderately aggregated, and substantial host mortality occurs at
relatively low parasite intensity.

@@

\caption{A) Five potential shapes for a host-survival functions. In the simulations we used a gradual survival function (dotted line), and moderate survival function (dashed line), and a steep survival function (solid line). The linear and immediate survival functions represent two potential extremes that we do not include in the simulations. For each of these survival functions and the parameter combinations described in the main text, we tested the Type I Error and Power of the Likelihood Method and Adjei Method. B) Gives the Type I Error of each method over a range of pre-mortality sample sizes with a pre-mortality mean parasite intensity ($\mu_p$) of 50 and pre-mortality parasite aggregation ($k_p$) at 0.5. The red line shows the pre-set significance level of 0.05. C) Gives the Power of each method for detecting PIHM over a range of post-mortality sample sizes for $\mu_p = 50$ and $k_p = 0.5$.  In general, the Likelihood Method has higher power and lower Type I Error than the Adjei Method.  See the SI 3 Fig 1 - 3 for Type I Error and Power results for all parameter combinations.}

@@

    \caption{Bias (\textbf{A}) and precision (\textbf{B}) (coefficient of variation) for the Likelihood Method and Adjei Method estimates of the $a$ parameter and the $LD_{50}$ of the host survival function based on simulated PIHM data over a range of post-mortality sample sizes. The pre-mortality parameters for this simulation were $\mu_p = 50$ and $k_p = 0.5$.  The figure shows the simulations for three different host survival functions (gradual, moderate, and steep), each with the same $LD_{50}$.  Bias and precision results of $LD_{50}$ and $a$ for all other parameter combinations can be found in SI 3 Fig 4 - 9.}

    \label{fig:question2}

### 2015-05-07 docs/supplementary_material.tex
Edited manuscript supplementary material and made a few changes to figures

% Figure and table formating
\usepackage{epsfig}
\usepackage{tabu}
\usepackage{rotating}
\usepackage{pbox}
\usepackage{framed, multicol}
\usepackage[framemethod=TikZ]{mdframed}
\usepackage{float}
\usepackage[left=1.25 in, right=1.25 in, top=1.25 in, bottom=1.25 in]{geometry}
\usepackage{csvsimple}

@@

We provide an implementation and unit tests of the Crofton Method Supplementary Information 3.  Figure \ref{fig:crof_test} visually shows the results of these unit tests.

@@

The Adjei Method for estimating PIHM has two steps.  The first
step is to estimate the parameters of the pre-mortality host-parasite
distribution using the Crofton Method.  The three parameters estimated are the
total number of hosts before mortality $N_p$,  the mean number of parasites per
host before mortality $\mu_p$, and the aggregation of parasites before
mortality given by the parameter $k_p$ from a negative binomial distribution.
When $k_p$ is small, parasites are highly aggregated among hosts and when
$k_p$ is large parasites are more evenly spread out \citep{Wilson2002}.  The implementation of the Crofton Method has been discussed at length elsewhere \citep[e.g.][]{Royce1990,Lester1984} and we provide a tested implementation of the method in SI 3.

@@

To estimate this function the Adjei Method proceeds as follows.  First, it
calculates the expected number of hosts with a given parasite load $x$ by using
the equation $g(x ; \mu_p, k_p) * N_p$, where $g(x ; \cdot)$ is the negative binomial pre-mortality distribution.  Second, the observed and predicted number of hosts
with $x$ parasites are paired as a single data point and the method then assumes that
this data point follows a binomial distribution with the total number of
``trials'' equal to the predicted number of hosts and the total number of
``successes'' equal to the observed number of hosts. In some cases, the
observed number of hosts is greater than the expected number of hosts and the
Adjei Method alters the data so that the observed is equal to the predicted
\citep{Adjei1986}.  After this questionable manipulation, the (observed, predicted) pairs are fit to a standard Generalized Linear Model \citep{McCullagh1989} with a binomial response variable and a logistic link function given by equation \ref{eq:logistic}.  This model provides estimates for parameters $a$, $b$ and $LD_{50}$.

@@

@@

See Figures 1 - 6.

@@

@@

@@

@@

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{/Users/mqwilber/Repos/parasite_mortality/results/compare_crofton.pdf}
    \caption{A comparison of this papers implementation of the Crofton Method with the results given in \cite{Crofton1971a}.  Three of the 6 stations fit by \cite{Crofton1971a} are shown here and all three show that the two implementations give very similar results.}
    \label{fig:crof_test}

>>>>

% Figure and table formating
\usepackage{epsfig}
\usepackage{tabu}
\usepackage{rotating}
\usepackage{pbox}
\usepackage{framed, multicol}
\usepackage[framemethod=TikZ]{mdframed}
\usepackage{float}
\usepackage[left=1.25 in, right=1.25 in, top=1.25 in, bottom=1.25 in]{geometry}

@@

We provide an implementation and unit tests of the Crofton Method Supplementary Information 4.  Figure \ref{fig:crof_test} visually shows that our implementation of the Crofton Method agrees with results previously published by \cite{Crofton1971a}.

@@

The Adjei Method for estimating PIHM has two steps \citep{Adjei1986}.  The first
step is to estimate the parameters of the pre-mortality host-parasite
distribution using the Crofton Method.  The three parameters estimated are the
total number of hosts before mortality $N_p$,  the mean number of parasites per
host before mortality $\mu_p$, and the aggregation of parasites before
mortality given by the parameter $k_p$ from a negative binomial distribution.
When $k_p$ is small, parasites are highly aggregated among hosts and when
$k_p$ is large parasites are more evenly spread out \citep{Wilson2002}.  The implementation of the Crofton Method has been discussed at length elsewhere \citep[e.g.][ and above]{Royce1990,Lester1984} and we provide a tested implementation of the method in SI 4.

@@

To estimate this function, the Adjei Method first
calculates the expected number of hosts with a given parasite load $x$ by using
the equation $g(x ; \mu_p, k_p) * N_p$, where $g(x ; \cdot)$ is the negative binomial pre-mortality distribution.  Second, the observed and predicted number of hosts
with $x$ parasites are paired as a single data point and the method then assumes that
this data point follows a binomial distribution with the total number of
``trials'' equal to the predicted number of hosts and the total number of
``successes'' equal to the observed number of hosts. In some cases, the
observed number of hosts is greater than the expected number of hosts and the
Adjei Method alters the data so that the observed is equal to the predicted
\citep{Adjei1986}.  After this questionable manipulation, the (observed, predicted) pairs are fit to a standard Generalized Linear Model \citep{McCullagh1989} with a binomial response variable and a logistic link function given by equation \ref{eq:logistic}.  This model provides estimates for parameters $a$, $b$ and $LD_{50}$.

@@

% \section*{Appendix 3: Implementation of the Likelihood Method}

% As described in the main text, the probability mass function for the likelihood method is given by

% \begin{equation}
%     P(x | \text{survival}) = \dfrac{P(\text{survival} | x) * P(x)}{P(\text{survival})}
%     \label{eq:concept}
% \end{equation}

% One can see that $P(\text{survival} | x)$ is the survival function $h(x; a, b)$, $P(x)$ is the pre-mortality parasite distribution $g(x; \mu_p, k_p)$ and $P(\text{survival}) = \sum_{x=0}^{\infty} P(\text{survival} | x) * P(x) =  \sum_{x=0}^{\infty} h(x; a, b)  * g(x; \mu_p, k_p)$. Therefore equation \ref{eq:concept} can be written as

% \begin{equation}
%     P(x | \text{survival}) = \dfrac{h(x; a, b)  * g(x; \mu_p, k_p)}{\sum_{x=0}^{\infty} h(x; a, b)  * g(x; \mu_p, k_p)}
%     \label{eq:dist}
% \end{equation}

% Using this equation, we seek to find estimates for $\mu_p$, $k_p$, $a$, and $b$
% that maximize the likelihood of equation \ref{eq:dist} given a host-parasite
% dataset. The first approach is use a standard maximization algorithm to try to
% find all four parameters.  However, for small number of hosts and/or a gradual
% survival function, the gradient of the likelihood will not contain much
% information (check this) and the maximization will likely fail or give
% unrealistic results. An alternative approach would be to parameterize $\mu_p$
% and $k_p$ using the Crofton Method and then use equation \ref{eq:dist} to find the values for $a$ and $b$ that maximize the likelihood of a host-parasite dataset.

@@

See Figures 1 - 9.

@@

    \includegraphics[width=\textwidth]{/Users/mqwilber/Repos/parasite_mortality/results/typeIpower_figure_for_mu10}

    \caption{The type I error rate and the power of the Likelihood Method (solid line) and the Adjei Method (dashed lines) when $\mu_p = 10$ for various shapes of the host survival function and levels of aggregation $k_p$.  The first column gives the type I error rate of each method for falsely detecting PIHM when none is present.  The red line gives the the pre-set type I error rate of $\alpha = 0.05$.  The second column gives the power of a given method to detect PIHM when it is actually occurring. }
    \label{fig:typeI10}

@@

    \includegraphics[width=\textwidth]{/Users/mqwilber/Repos/parasite_mortality/results/bais_prec_figure_for_ld50_mu10}

    \caption{The bias and the precision of the Likelihood Method (solid line) and the Adjei Method (dashed lines) when $\mu_p = 10$ for various shapes of the host survival function and levels of aggregation $k_p$ when estimating $LD_{50}$.  The first column gives the bias of each method's $LD_{50}$ estimate over 150 simulations. The second column gives the precision of each method's $LD_{50}$ estimate over 150 simulations.}

    \label{fig:biasld50_10}

@@

    \includegraphics[width=\textwidth]{/Users/mqwilber/Repos/parasite_mortality/results/bais_prec_figure_for_a_mu10}

    \caption{The bias and the precision of the Likelihood Method (solid line) and the Adjei Method (dashed lines) when $\mu_p = 10$ for various shapes of the host survival function and levels of aggregation $k_p$ when estimating the $a$ parameter of the host survival function.  The first column gives the bias of each method's $a$ estimate over 150 simulations. The second column gives the precision of each method's $a$ estimate over 150 simulations.}

    \label{fig:biasa_10}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{/Users/mqwilber/Repos/parasite_mortality/results/compare_crofton.pdf}
    \caption{A comparison of this papers implementation (solid line, circles) of the Crofton Method with the results given in \cite{Crofton1971a} (dashed line, diamonds).  Figure A compares the predicted number of hosts in a population pre-mortality ($N_p$). Figure B compares the predicted parasite aggregation pre-mortality ($k_p$).  Figure C compares the $\chi^2$ statistic for each implementation.  Three of the 6 stations fit by \citeauthor{Crofton1971a} are shown here and all show that our implementation gives very similar results to those given by \citeauthor{Crofton1971a}.}
    \label{fig:crof_test}
